---
title: "Optimizing Portfolio Risk of Cryptocurrencies Using Data-Driven Risk Measures"
author: "Sulalitha Bowala and Japjeet Singh"
date: "17/08/2022"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Portfolio optimization is an important topic in Finance. Modern portfolio theory (MPT) states that investors are risk averse and given a level of risk, they will choose the portfolios that offer the most return. To do that we need to optimize the portfolios.

To perform the optimization we will need

- To download the price data of the assets

- Assign random weights to the assets

- Calculate daily portfolio return, sd, kurtosis, ddve, sign correlation and t df

- Use the daily portfolio return, ddve, sign correlation and t df to pick up minimum risk and tangency portfolio and determine the optimal weights

- Use the optimal weights of each portfolio to calculate the annualized portflio return, sd and Sharpe ratio to compare all the portfolios

- Use GA to compare with the random weights algorithm

So lets begin

## Downloading data

First lets load our packages

```{r}
list.of.packages <- c('tidyverse','tidyquant', 'plotly','timetk','GA','xtable', 'textreadr','rvest','fGarch',"dplyr", "dygraphs", "quantmod", "TTR", 'zoo', 'tseries', 'fGarch','PEIP','tidyverse','gridExtra', 'gdata', 'xtable',"dygraphs") 
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages) > 0) {install.packages(new.packages)}
lapply(list.of.packages, require, character.only=T)
```

```{r}
# Load all the required functions needed get the results
## function to generate weight
# get_weights <- function(N){
#  return(diff(c(0, sort(runif(N-1, min = 0, max = 1)), 1)))
# }
get_weights <- function(N){
  w<- runif(N, min = 0, max = 1)
  return(w/sum(w))
}
```

Next lets select a few stocks to build our portfolios.

We will choose some stocks.

Lets download the price data.

```{r}

# Read and Store data in RStudio Environment

AAPLdata <- read.csv('AAPL_data_hourly.csv')

AAPL1=AAPLdata$Adj.Close

AMZNdata <- read.csv('AMZN_data_hourly.csv')

AMZN1=AMZNdata$Adj.Close

MSFTdata <- read.csv('MSFT_data_hourly.csv')

MSFT1=MSFTdata$Adj.Close

ADBEdata <- read.csv('ADBE_data_hourly.csv')

ADBE1=ADBEdata$Adj.Close

MRVLdata <- read.csv('MRVL_data_hourly.csv')

MRVL1=MRVLdata$Adj.Close


price_data1=cbind.data.frame(AAPL1, AMZN1, MSFT1, ADBE1, MRVL1)
names(price_data1)<-c("AAPL","AMZN","MSFT","ADBE","MRVL")
price_data1 <- na.omit(price_data1)

# Observe data

head(price_data1)
tail(price_data1)

# Plot the data (Only for AAPL. Change name to obtain plot for others)

plot(price_data1$AAPL, type = "l", ylab='', main='Price (AAPL)', cex.main = 2, cex.lab = 1.5, cex.axis = 1.5, lwd=4.0, col = "blue")
```


```{r}
# Organize and calculate returns

ret_tidy1 = apply(price_data1,2, log)
head(ret_tidy1)
ret_tidy2 = diff(ret_tidy1)
head(ret_tidy2)
ret_tidy = exp (ret_tidy2) - 1 #simple returns

head (ret_tidy)
tail(ret_tidy)

ret_xts=ret_tidy
```


```{r}
## remove the first row of zero simple returns for all the columns
asset_returns <- ret_xts[-1,]
# Divide the data fro taining and testing
nrow(asset_returns)
smp_siz = floor(0.7*nrow(asset_returns))
train = asset_returns[1:smp_siz,] 
test = asset_returns[-(1:smp_siz),]
tail (train)
head (test)
tail(test)
nasset <- ncol(asset_returns)
```

```{r}
# skewness correlation
skewrho <- function(X){
  skewrho.cor <- cor(X-mean(X), (X-mean(X))^2)
  return(skewrho.cor)
}

# sign correlation
rho.cal<-function(X){
  rho.hat<-cor(sign(X-mean(X)), X-mean(X))
  return(rho.hat)
}

# volatlity correlation
rho.vol<-function(X){
  rho.vol<-cor(abs(X-mean(X)), (X-mean(X))^2)
  return(rho.vol)
}
```


Simulation study for sign correlation and volatility correlation
```{r}
# simulate normal, t(2), t(3), t(4), t(5)
sample <- 8000
sim.n <- rnorm (sample)     # sign correlation of a normal distribution is sqrt(2/pi)=0.7979
sim.t25 <- rt (sample, df = 2.5)
sim.t3 <- rt (sample, df = 3)
sim.t35 <- rt (sample, df = 3.5)
sim.t4 <- rt (sample, df = 4)
sim.t5 <- rt (sample, df = 5)
data <- cbind (sim.t25, sim.t3, sim.t35, sim.t4, sim.t5, sim.n)

skewrho<-apply(as.matrix(data), MARGIN=2, FUN=skewrho)
rhosign<-apply(as.matrix(data), MARGIN=2, FUN=rho.cal)
rhovol<-apply(as.matrix(data), MARGIN=2, FUN=rho.vol)

assetsummary<-data.frame(apply(data, 2, mean), apply(data, 2, sd), apply(data, 2, skewness), apply(data, 2, kurtosis), skewrho, rhovol, rhosign)
xtable(assetsummary, digits=4)
```

```{r}
##summary statistics of algo returns
rhosign<-apply(as.matrix(train), MARGIN=2, FUN=rho.cal)
rhovol<-apply(as.matrix(train), MARGIN=2, FUN=rho.vol)
assetsummary<-data.frame(apply(train, 2, mean), apply(train, 2, sd), rhovol, rhosign, apply(train, 2, skewness),
                 apply(train, 2, kurtosis))
xtable(assetsummary, digits=4)
```

```{r}
plot(train, legend.loc=1)
```

Lets calculate annualized portfolio return, risk, and gamma from the simulated portfolio  returns with portfolio weights.
(simulated weights)

```{r}
## portfolio return, sd and gamma
## w is the random weight
## data = train or test
portfolio_info = function(w, data){
  port.data <- data%*%as.vector(w)
  port.cdf <- ecdf(port.data)
  port.return <- mean (port.data)
  port.sd <- sd (port.data)
  port.signrho <- cor (port.data - port.return, sign(port.data - port.return))
# port.signrho3 <- cor (sign(port.data - port.return), (port.data - port.return)^3)
# port.skewrho <- cor (port.data - port.return, (port.data - port.return)^2)
  port.volcor <- cor (abs(port.data - port.return), (port.data - port.return)^2) #volatlity correlation
  port.skewness <- skewness (port.data) #mu_3/sigma^3
  port.kurtosis <- kurtosis (port.data) #excess kurtosis mu_4/sigma^4 - 3
  return(c(port.return, port.sd, port.volcor, port.signrho, port.cdf(port.return), port.skewness, port.kurtosis))
}
```

```{r}
stat<-matrix(0, nrow = 5, ncol = 7)
weight<-matrix(0, nrow = 5, ncol = 5)
for (i in 1:5){
weight[i, ] <- get_weights(nasset)
stat[i, ] <- portfolio_info (weight[i, ], train)
}
xtable(weight, digits = 4)
xtable(stat, digits = 4)
```

Check for the portfolio sd can be calcualted by both the formula and sd of the simulated portfolio.

We have everything we need to perform our optimization. All we need now is to run this code on 8000 random portfolios. For that we will use a for loop.

Before we do that, we need to create empty vectors and matrix for storing our values.

```{r}
num_port <- 8000
nasset <- 5

# Creating a matrix to store the weights

all_wts1 <- matrix(nrow = num_port,
                  ncol = nasset)

# Creating an empty vector to store
# 8000 Portfolio returns

port_returns <- vector('numeric', length = num_port)

# Creating an empty vector to store
# 8000 Portfolio variances

port_risk.var1 <- vector('numeric', length = num_port)
port_risk.var2 <- vector('numeric', length = num_port)
port_risk.var3 <- vector('numeric', length = num_port)
port_risk.var4 <- vector('numeric', length = num_port)
port_risk.mad <- vector('numeric', length = num_port)

Sharpe_ratio.sd1 <- vector('numeric', length = num_port)
Sharpe_ratio.sd2 <- vector('numeric', length = num_port)
Sharpe_ratio.sd3 <- vector('numeric', length = num_port)
Sharpe_ratio.sd4 <- vector('numeric', length = num_port)
Sharpe_ratio.mad <- vector('numeric', length = num_port)
```

Next lets run the for loop 8000 times.

```{r}
port.info <- matrix(0, nrow = 8000, ncol = 7)

ptm <- proc.time()

for (i in seq_along(port_returns)) {
  
  wts <- get_weights(nasset)
  
  # Storing weight in the matrix
  all_wts1[i,] <- wts
  
  # Portfolio returns
  
  port.info [i, ]<- portfolio_info (wts, train)
  
  # Storing Portfolio Returns values
  port_returns[i] <- port.info[i, 1]
  
  # Creating and storing portfolio risk
  port_risk.var1 [i] <- port.info[i, 2]
  port_risk.var2 [i] <- sqrt(1 - port.info[i, 3]^2)*port.info[i, 2]
  port_risk.var3 [i] <- sqrt(1 - port.info[i, 4]^2)*port.info[i, 2]
  port_risk.var4 [i] <- sqrt(1 - port.info[i, 3]^2)*sqrt(1 - port.info[i, 4]^2)*port.info[i, 2]
  port_risk.mad [i] <- 2*port.info[i, 2]*port.info[i, 4]*sqrt(port.info[i, 5]*(1-port.info[i, 5]))
  
  # Creating and storing Portfolio Sharpe Ratios
  # Assuming 0% Risk free rate
  
  Sharpe_ratio.sd1 [i] <- port_returns[i]/port_risk.var1 [i]
  Sharpe_ratio.sd2 [i] <- port_returns[i]/port_risk.var2 [i]
  Sharpe_ratio.sd3 [i] <- port_returns[i]/port_risk.var3 [i]
  Sharpe_ratio.sd4 [i] <- port_returns[i]/port_risk.var4 [i]
  Sharpe_ratio.mad [i] <- port_returns[i]/port_risk.mad [i]
}
proc.time()-ptm
```

```{r}
port.info.data <- as.data.frame(port.info)

ggplot(port.info.data, aes(x=V6, y=V1)) + geom_point(color="blue", alpha=0.5) +geom_smooth(color="darkred") + xlab ("Skewness") + ylab ("Return")

ggplot(port.info.data, aes(x=V7, y=V1)) + geom_point(color="blue", alpha=0.5) +geom_smooth(color="darkred") + xlab ("Kurtosis") + ylab ("Return")

ggplot(port.info.data, aes(x=V3, y=V6)) + geom_point(color="blue", alpha=0.5) +geom_smooth(color="darkred") + xlab ("Volatlity Correlation") + ylab ("Skewness")

ggplot(port.info.data, aes(x=V3, y=V7)) + geom_point(color="blue", alpha=0.5) +geom_smooth(color="darkred") + xlab ("Volatlity Correlation") + ylab ("Kurtosis")

ggplot(port.info.data, aes(x=V3, y=V1)) + geom_point(color="blue", alpha=0.5) +geom_smooth(color="darkred") + xlab ("Volatlity Correlation") + ylab ("Return")

ggplot(port.info.data, aes(x=V3, y=V2)) + geom_point(color="blue", alpha=0.5) +geom_smooth(color="darkred") + xlab ("Volatlity Correlation") + ylab ("Volatility")
```

```{r}
ggplot(port.info.data, aes(x=V2, y=V1)) + geom_point(color="blue", alpha=0.5) +geom_smooth(color="darkred") + xlab ("Volatlity") + ylab ("Return")

ggplot(port.info.data, aes(x=V3, y=V2)) + geom_point(color="blue", alpha=0.5) +geom_smooth(color="darkred") + xlab ("Volatlity Correlation") + ylab ("Volatlity")

ggplot(port.info.data, aes(x=V4, y=V2)) + geom_point(color="blue", alpha=0.5) +geom_smooth(color="darkred") + xlab ("Sign Correlation") + ylab ("Volatility")

ggplot(port.info.data, aes(x=V4, y=V6)) + geom_point(color="blue", alpha=0.5) +geom_smooth(color="darkred") + xlab ("Sign Correlation") + ylab ("Skewness")

ggplot(port.info.data, aes(x=V4, y=V7)) + geom_point(color="blue", alpha=0.5) +geom_smooth(color="darkred") + xlab ("Sign Correlation") + ylab ("Kurtosis")

ggplot(port.info.data, aes(x=V4, y=V1)) + geom_point(color="blue", alpha=0.5) +geom_smooth(color="darkred") + xlab ("Sign Correlation") + ylab ("Return")

```

We now create a data table to store all the values together (using sd).

```{r}
# Storing the values in the table (5 columns and 8000 rows)
portfolio_values1 <- tibble(Return = port_returns,
                  Risk1 = port_risk.var1,
                  Risk2 = port_risk.var2,
                  Risk3 = port_risk.var3,
                  Risk4 = port_risk.var4,
                  Risk5 = port_risk.mad,
                  SharpeRatio1 = Sharpe_ratio.sd1,
                  SharpeRatio2 = Sharpe_ratio.sd2,
                  SharpeRatio3 = Sharpe_ratio.sd3,
                  SharpeRatio4 = Sharpe_ratio.sd4,
                  SharpeRatio5 = Sharpe_ratio.mad,
                  )
# Converting matrix to a tibble and changing column names
all_wts1 <- tk_tbl(all_wts1)
```

```{r}
colnames(all_wts1) <- colnames(asset_returns)

# Combing all the values together
portfolio_values1 <- tk_tbl(cbind(all_wts1, portfolio_values1))
```

We have the weights in each asset with the risk and returns along with the Sharpe ratio of each portfolio. We use daily data to determine the portfolios.

Next lets look at the portfolios that matter the most.

```{r}
min_var1 <- portfolio_values1[which.min(portfolio_values1$Risk1),]
min_var2 <- portfolio_values1[which.min(portfolio_values1$Risk2),]
min_var3 <- portfolio_values1[which.min(portfolio_values1$Risk3),]
min_var4 <- portfolio_values1[which.min(portfolio_values1$Risk4),]
min_mad <- portfolio_values1[which.min(portfolio_values1$Risk5),]
max_sr1 <- portfolio_values1[which.max(portfolio_values1$SharpeRatio1),]
max_sr2 <- portfolio_values1[which.max(portfolio_values1$SharpeRatio2),]
max_sr3 <- portfolio_values1[which.max(portfolio_values1$SharpeRatio3),]
max_sr4 <- portfolio_values1[which.max(portfolio_values1$SharpeRatio4),]
max_sr5 <- portfolio_values1[which.max(portfolio_values1$SharpeRatio5),]
rbind(min_var1, min_var2, min_var3, min_var4, min_mad, max_sr1, max_sr2, max_sr3, max_sr4, max_sr5)
xtable(rbind(min_var1, min_var2, min_var3, min_var4, min_mad, max_sr1, max_sr2, max_sr3, max_sr4, max_sr5), digits = 6)
```

```{r}
p1 <- cbind(min_var1[1:5], 1764*min_var1[6], sqrt(1764)*min_var1[7], sqrt(1764)*min_var1[12])
p2 <- cbind(min_var2[1:5], 1764*min_var2[6], sqrt(1764)*min_var2[8], sqrt(1764)*min_var2[13])
p3 <- cbind(min_var3[1:5], 1764*min_var3[6], sqrt(1764)*min_var3[9], sqrt(1764)*min_var3[14])
p4 <- cbind(min_var4[1:5], 1764*min_var4[6], sqrt(1764)*min_var4[10], sqrt(1764)*min_var4[15])
p5 <- cbind(min_mad[1:5], 1764*min_mad[6], sqrt(1764)*min_mad[11], sqrt(1764)*min_mad[16])
xtable(t(rbind(as.numeric(p1), as.numeric(p2), as.numeric(p3), as.numeric(p4), as.numeric(p5))), digits = 5)
```

```{r}
p1 <- cbind(max_sr1[1:5], 1764*max_sr1[6], sqrt(1764)*max_sr1[7], sqrt(1764)*max_sr1[12])
p2 <- cbind(max_sr2[1:5], 1764*max_sr2[6], sqrt(1764)*max_sr2[8], sqrt(1764)*max_sr2[13])
p3 <- cbind(max_sr3[1:5], 1764*max_sr3[6], sqrt(1764)*max_sr3[9], sqrt(1764)*max_sr3[14])
p4 <- cbind(max_sr4[1:5], 1764*max_sr4[6], sqrt(1764)*max_sr4[10], sqrt(1764)*max_sr4[15])
p5 <- cbind(max_sr5[1:5], 1764*max_sr5[6], sqrt(1764)*max_sr5[11], sqrt(1764)*max_sr5[16])
xtable(t(rbind(as.numeric(p1), as.numeric(p2), as.numeric(p3), as.numeric(p4), as.numeric(p5))), digits = 5)
```

```{r}
nasset <- ncol(asset_returns)
w1 <- min_var1[, 1:nasset] %>% gather () %>% arrange(desc(value))
w2 <- min_var2[, 1:nasset] %>% gather () %>% arrange(desc(value))
w3 <- min_var3[, 1:nasset] %>% gather () %>% arrange(desc(value))
w4 <- min_var4[, 1:nasset] %>% gather () %>% arrange(desc(value))
w5 <- min_mad[, 1:nasset] %>% gather () %>% arrange(desc(value))
w6 <- max_sr1[, 1:nasset] %>% gather () %>% arrange(desc(value))
w7 <- max_sr2[, 1:nasset] %>% gather () %>% arrange(desc(value))
w8 <- max_sr3[, 1:nasset] %>% gather () %>% arrange(desc(value))
w9 <- max_sr4[, 1:nasset] %>% gather () %>% arrange(desc(value))
w10 <- max_sr5[, 1:nasset] %>% gather () %>% arrange(desc(value))

xtable(cbind(head (w1, 10), head (w2, 10), head (w3, 10), head (w4, 10), head (w5, 10), head (w6, 10), head (w7, 10), head (w8, 10), head (w9, 10), head (w10, 10)), digits = 4)
```

Lets plot the weights of each portfolio. First with the minimum variance portfolio.

```{r}
p1 <- min_var4 %>%
  gather(AAPL:MRVL, key = Asset,
         value = Weights) %>%
  mutate(Asset = as.factor(Asset)) %>%
  ggplot(aes(x = fct_reorder(Asset,Weights), y = Weights, fill = Asset)) +
  geom_bar(stat = 'identity') +
  theme_minimal() +
  labs(x = 'Assets', y = 'Weights', title = "Minimum Risk Portfolio Weights") +
  scale_y_continuous(labels = scales::percent) 
ggplotly(p1)
```

```{r}
p2 <- max_sr4 %>%
  gather(c('AAPL', 'AMZN', 'MSFT', 'ADBE', 'MRVL'), key = Asset,
         value = Weights) %>%
  mutate(Asset = as.factor(Asset)) %>%
  ggplot(aes(x = fct_reorder(Asset, Weights), y = Weights, fill = Asset)) +
  geom_bar(stat = 'identity') +
  theme_minimal() +
  labs(x = 'Assets', y = 'Weights', title = "Tangency Portfolio Weights") +
  scale_y_continuous(labels = scales::percent) 
ggplotly(p2)
```

```{r}
#convert daily return, risk, SR to annualized ones

portfolio_values1_annual <- portfolio_values1 %>% mutate(Return = Return * 1764) %>% mutate(Risk1 = Risk1 * sqrt(1764), Risk2 = Risk2 * sqrt(1764), Risk3 = Risk3 * sqrt(1764), Risk4 = Risk4 * sqrt(1764), Risk5 = Risk5 * sqrt(1764)) %>% mutate(SharpeRatio1 = SharpeRatio1 * sqrt(1764), SharpeRatio2 = SharpeRatio2 * sqrt(1764), SharpeRatio3 = SharpeRatio3 * sqrt(1764), SharpeRatio4 = SharpeRatio4 * sqrt(1764), SharpeRatio5 = SharpeRatio5 * sqrt(1764))
```

```{r}
min_var1.a <- portfolio_values1_annual[which.min(portfolio_values1_annual$Risk1),]
min_var2.a <- portfolio_values1_annual[which.min(portfolio_values1_annual$Risk2),]
min_var3.a <- portfolio_values1_annual[which.min(portfolio_values1_annual$Risk3),]
min_var4.a <- portfolio_values1_annual[which.min(portfolio_values1_annual$Risk4),]
min_mad.a <- portfolio_values1_annual[which.min(portfolio_values1_annual$Risk5),]
max_sr1.a <- portfolio_values1_annual[which.max(portfolio_values1_annual$SharpeRatio1),]
max_sr2.a <- portfolio_values1_annual[which.max(portfolio_values1_annual$SharpeRatio2),]
max_sr3.a <- portfolio_values1_annual[which.max(portfolio_values1_annual$SharpeRatio3),]
max_sr4.a <- portfolio_values1_annual[which.max(portfolio_values1_annual$SharpeRatio4),]
max_sr5.a <- portfolio_values1_annual[which.max(portfolio_values1_annual$SharpeRatio5),]

rbind(min_var1.a, min_var2.a, min_var3.a, min_var4.a, min_mad.a, max_sr1.a, max_sr2.a, max_sr3.a, max_sr4.a, max_sr5.a)
```

```{r}
p1 <- portfolio_values1_annual %>%
  ggplot(aes(x = Risk1, y = Return, color = SharpeRatio1)) +
  geom_point(alpha = 0.4)+
  theme_classic() +
  scale_y_continuous(labels = scales::percent) +
  scale_x_continuous(labels = scales::percent) +
  labs(x = 'Annualized Risk (SD)',
       y = 'Annualized Returns',
       title = "Portfolio Optimization & Efficient Frontier") +
  geom_point(aes(x = Risk1,
                 y = Return), data = min_var1.a, color = 'orange') +
  geom_point(aes(x = Risk1,
                 y = Return), data = max_sr1.a, color = 'orange4', shape = 18)
ggplotly(p1)
```


```{r}
p2 <- portfolio_values1_annual %>%
  ggplot(aes(x = Risk2, y = Return, color = SharpeRatio2)) +
  geom_point(alpha = 0.4)+
  theme_classic() +
  scale_y_continuous(labels = scales::percent) +
  scale_x_continuous(labels = scales::percent) +
  labs(x = 'Annualized Risk (VEV)',
       y = 'Annualized Returns',
       title = "Portfolio Optimization & Efficient Frontier") +
  geom_point(aes(x = Risk2,
                 y = Return), data = min_var2.a, color = 'green') +
  geom_point(aes(x = Risk2,
                 y = Return), data = max_sr2.a, color = 'green4', shape = 18)
ggplotly(p2)
```
```{r}
p3 <- portfolio_values1_annual %>%
  ggplot(aes(x = Risk3, y = Return, color = SharpeRatio3)) +
  geom_point(alpha = 0.4)+
  theme_classic() +
  scale_y_continuous(labels = scales::percent) +
  scale_x_continuous(labels = scales::percent) +
  labs(x = 'Annualized Risk (VES)',
       y = 'Annualized Returns',
       title = "Portfolio Optimization & Efficient Frontier") +
  geom_point(aes(x = Risk3,
                 y = Return), data = min_var3.a, color = 'red') +
  geom_point(aes(x = Risk3,
                 y = Return), data = max_sr3.a, color = 'red4', shape = 18)
ggplotly(p3)
```

```{r}
p4 <- portfolio_values1_annual %>%
  ggplot(aes(x = Risk4, y = Return, color = SharpeRatio4)) +
  geom_point(alpha = 0.4)+
  theme_classic() +
  scale_y_continuous(labels = scales::percent) +
  scale_x_continuous(labels = scales::percent) +
  labs(x = 'Annualized Risk (VESV)',
       y = 'Annualized Returns',
       title = "Portfolio Optimization & Efficient Frontier") +
  geom_point(aes(x = Risk4,
                 y = Return), data = min_var4.a, color = 'purple') +
  geom_point(aes(x = Risk4,
                 y = Return), data = max_sr4.a, color = 'purple4', shape = 18)
ggplotly(p4)
```

```{r}
p5 <- portfolio_values1_annual %>%
  ggplot(aes(x = Risk5, y = Return, color = SharpeRatio5)) +
  geom_point(alpha = 0.4)+
  theme_classic() +
  scale_y_continuous(labels = scales::percent) +
  scale_x_continuous(labels = scales::percent) +
  labs(x = 'Annualized Risk (MAD)',
       y = 'Annualized Returns',
       title = "Portfolio Optimization & Efficient Frontier") +
  geom_point(aes(x = Risk5,
                 y = Return), data = min_mad.a, color = 'blue') +
  geom_point(aes(x = Risk5,
                 y = Return), data = max_sr5.a, color = 'blue4', shape = 18)
ggplotly(p5)
```

## Plots cummulative returns of the test sample

```{r}
MVP1 <- test%*%as.vector(as.numeric(min_var1[1:nasset]))
MVP2 <- test%*%as.vector(as.numeric(min_var2[1:nasset]))
MVP3 <- test%*%as.vector(as.numeric(min_var3[1:nasset]))
MVP4 <- test%*%as.vector(as.numeric(min_var4[1:nasset]))
MVP5 <- test%*%as.vector(as.numeric(min_mad[1:nasset]))
TP1<-test%*%as.vector(as.numeric(max_sr1[1:nasset]))
TP2<-test%*%as.vector(as.numeric(max_sr2[1:nasset]))
TP3<-test%*%as.vector(as.numeric(max_sr3[1:nasset]))
TP4<-test%*%as.vector(as.numeric(max_sr4[1:nasset]))
TP5<-test%*%as.vector(as.numeric(max_sr5[1:nasset]))
EWQ<-test%*%as.vector(rep(1/nasset, nasset))
assets <- c("MVP1", "MVP2", "MVP3", "MVP4", "MVP5", "TP1", "TP2", "TP3", "TP4", "TP5", "EWQ")

#Portfolios <- merge(test[, 1], cumsum(MVP1), cumsum(MVP2), cumsum(MVP3), cumsum(MVP4), cumsum(MVP5), cumsum(TP1), cumsum(TP2), cumsum(TP3), cumsum(TP4), cumsum(TP5), cumsum(EWQ))[, -c(1)]

Portfolios <- cbind.data.frame(cumsum(MVP1), cumsum(MVP2), cumsum(MVP3), cumsum(MVP4), cumsum(MVP5), cumsum(TP1), cumsum(TP2), cumsum(TP3), cumsum(TP4), cumsum(TP5), cumsum(EWQ))

colnames(Portfolios) <- assets
```

```{r}
row.names(Portfolios) <- MSFTdata$X[-(1:2330)]
dygraph(Portfolios, main = 'Cummulative Returns for Test Period')%>%
dySeries('MVP1', label = 'MVP', col = "orange") %>%
dySeries('MVP2', label = 'MRP2', col = "green") %>%
dySeries('MVP3', label = 'MRP3', col = "red") %>%  
dySeries('MVP4', label = 'MRP4', col = "purple") %>%
dySeries('MVP5', label = 'MRP5', col = "blue") %>%
dySeries('TP1', label = 'TP', col = "orange", drawPoints = TRUE) %>% 
dySeries('TP2', label = 'MRRP2', col = "green", drawPoints = TRUE) %>%
dySeries('TP3', label = 'MRRP3', col = "red", drawPoints = TRUE) %>%  
dySeries('TP4', label = 'MRRP4', col = "purple", drawPoints = TRUE) %>% 
dySeries('TP5', label = 'MRRP5', col = "blue", drawPoints = TRUE) %>%  
dySeries('EWQ', label = 'EWQ', col = "black") %>% 
dyRangeSelector(height = 30)%>%
  dyLegend(width = 500)
```




